\begin{thebibliography}{9}

\bibitem{Bitcoin} NAKAMOTO, S. Bitcoin: A Peer-to-Peer Electronic Cash System, 2008.

\bibitem{Health} LINN, L. A., AND KOO, M. B. Blockchain for health data and its potential use in health it and health care related research. In ONC/NIST Use of Blockchain for Healthcare and Research Workshop. Gaithersburg,
Maryland, United States: ONC/NIST (2016)

\bibitem{Privacy} JUAN DELACRUZ, I. B. Blockchain is tackling the challenge of data sharing in government, May 2018

\bibitem{ByzCoin Impl} DEDIS, ByzCoin, accessed 11.02.2019, <\url{https://github.com/dedis/cothority/blob/master/byzcoin/README.md}>

\bibitem{ByzCoin Figure} DEDIS, ByzCoin Figure, accessed 08.03.2019, <\url{https://raw.githubusercontent.com/dedis/cothority/master/byzcoin/ByzCoin.png}>

\bibitem{Calypso Implementation} DEDIS, Calypso, accessed 12.02.2019, <\url{https://github.com/dedis/cothority/tree/master/calypso}>

\bibitem{Calypso} E. Kokoris-Kogias, E. Ceyhun Alp, S. Deepthy Siby, N. Gailly, L. Gasser, P. Jovanovic, E. Syta, and B. Ford. CALYPSO: Auditable Sharing of Private Data over Blockchains, 2018

\bibitem{Chainiac} NIKITIN, K., KOKORIS-KOGIAS, E., JOVANOVIC, P., GAILLY,
N., GASSER, L., KHOFFI, I., CAPPOS, J., AND FORD, B. CHAINIAC:
Proactive Software-Update Transparency via Collectively Signed Skipchains and Verified Builds. In 26th USENIX Security Symposium (USENIX Security 17) (2017), USENIX Association, pp. 1271–1287.

\bibitem{Contracts} DEDIS, Contracts, accessed 11.02.2019, <\url{https://github.com/dedis/cothority/blob/master/byzcoin/Contracts.md}>

\bibitem{Cothority} DEDIS, Cothority, accessed 11.02.2019, <\url{https://github.com/dedis/cothority}>

\bibitem{Template} DEDIS, Cothority Template, accessed 30.09.2018, <\url{https://github.com/dedis/cothority\_template}>

\bibitem{Darc} DEDIS, Darc, accessed 06.02.2019, <\url{https://github.com/dedis/cothority/tree/master/darc}> 

\bibitem{SkipLists} J. Ian Munro, Thomas Papadakis, and Robert Sedgewick.
Deterministic Skip Lists. In Proceedings of the Third Annual ACM-SIAM
Symposium on Discrete Algorithms, SODA ’92, pages 367–375,
14 Philadelphia, PA, USA, 1992. Society for Industrial and Applied Mathematics

\bibitem{Attacks2} KARAME, G. O., ANDROULAKI, E., AND CAPKUN, S. Double-spending fast payments in Bitcoin. In 19th ACM Conference on Computer and communications security (2012), ACM

\bibitem{ByzCoin} E. Kokoris-Kogias, P. Jovanovic, N. Gailly, I. Khoffi, L. Gasser, and B. Ford. Enhancing Bitcoin Security and Performance with Strong
Consistency via Collective Signing. In Proceedings of the 25th USENIX
Conference on Security Symposium, 2016

\bibitem{Ethereum} WOOD, G. Ethereum: A Secure Decentralised Generalised Transaction Ledger. Ethereum Project Yellow Paper (2014)

\bibitem{Costs} European Parliament, created 29.05.2018, accessed 05.02.2019, <\url{http://www.europarl.europa.eu/news/en/headlines/society/20180525STO04312/fighting-mileage-fraud-on-used-cars}>

\bibitem{CoSi} SYTA, E., TAMAS, I., VISHER, D., WOLINSKY,
D. I., L., GAILLY, N., KHOFFI, I., AND FORD, B.
Keeping Authorities “Honest or Bust” with Decentralized
Witness Cosigning. In 37th IEEE Symposium
on Security and Privacy (May 2016)

\bibitem{Attacks1} EYAL, I., AND SIRER, E. G. Majority is not enough: Bitcoin mining is vulnerable. In Financial Cryptography and Data Security. Springer, 2014

\bibitem{Medical Data} AZARIA, A., EKBLAW, A., VIEIRA, T., AND LIPPMAN, A. Medrec: Using blockchain for medical data access and permission management. In
Open and Big Data (OBD), International Conference on (2016), IEEE, pp. 25–30

\bibitem{Mininet} DEDIS, Mininet, accessed 25.02.2019, <\url{https://github.com/dedis/onet/blob/master/simul/platform/MININET.md}>

\bibitem{OmniLedger} KOKORIS-KOGIAS, E., JOVANOVIC, P., GASSER, L., GAILLY, N., SYTA, E., AND FORD, B. OmniLedger: A Secure, Scale-Out, Decentralized Ledger via Sharding. In Security and Privacy (SP), 2018 IEEE Symposium on (2018), Ieee

\bibitem{Onet Simulation} DEDIS, Onet Simulation, accessed 25.02.2019, <\url{https://godoc.org/github.com/dedis/onet\#Simulation}>

\bibitem{PBFT} M. Castro and B. Liskov. Practical Byzantine Fault Tolerance. In 3rd USENIX Symposium on Operating Systems Design and Implementation
(OSDI), Feb. 1999

\bibitem{Protocol Buffers} Google, Protocol Buffers, accessed 15.02.2019,
<\url{https://developers.google.com/protocol-buffers/}>

\bibitem{Merkle} R.C. Merkle, "Protocols for public key cryptosystems," In Proc. 1980
Symposium on Security and Privacy, IEEE Computer Society, pages 122-
133, April 1980

\bibitem{Simulation} DEDIS, Simulation, accessed 25.02.2019, <\url{https://github.com/dedis/cothority\_template/tree/master/simulation}>

\bibitem{Skipchain Explorer} DEDIS, Skipchain Explorer, accessed 24.02.2019, <\url{https://github.com/dedis/student\_18\_explorer}> 










\end{thebibliography}